A Minimal Book Example

### 2020-03-02 manuscript/drafts/manuscript.Rmd
update manuscript and meeting notes

# Introduction
SR are booming
ML tools as well

@@

# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
annotated include/exclude

## Datasets
The data consists of five open datasets on systematic reviews from various research areas. 
All datasets are openly available.
The raw files were preprocessed. Duplicate entries were removed.
Entries with missing abstracts were removed. 
Preprocessing scripts can be found on the GitHub repository

Descriptive statistics on the five systematic reviews can be found in `r table_nums("datasets", display = "cite")`.

@@

### Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets.

#### ACE
The ACEInhibitors dataset from the study by [@Cohen2006]. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

@@

#### ptsd
The review  
The data

#### hall 
The review [@Hall2012], is reviewed in [@Yu2018a].

#### nudging
The review [@Nagtegaal2019]
The data [@Nagtegaal2019a]

Paper says: 
- systematic search n = 2006
- full text screening n = 377
- included in synthesis n = 100

Open data online says:

- systematic search n = 
- full text screening n = 
- included in synthesis n = 101 (18?)

abstract excel sheet private says: 
- systematic search n = 2018
- full text screening n = 
- included in synthesis n = 118

@@

## Stage 2: simulation
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

### Outcomes 
Several metrics are used to compare performance of different models over datasets,

@@

# Appendix A - list of definitions

>>>>

#### Introduction 
#### Methods
A convenience sample of 5 existing systematic reviews on varying topics was collected.

#### Results
#### Discussion

\newpage
# Introduction
SR are booming
ML tools as well
Literature reviews 
machine learning algorithms have been proposed to reduce workload in abstract screening.

- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
- justification - 
- background 
- guidance to reader 
- summary/conclusion

@@

\newpage
# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate.

## Datasets
The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

#### software 
A review on fault prediction in software engineering by [@Hall2012]. 
The dataset is reviewed from [@Yu2018a] who collected datasets on literature reviews from the software engineering field.

#### nudging
review [@Nagtegaal2019]
The data [@Nagtegaal2019a]

#### ptsd
The review [@vandeSchoot2018]
The data [@Winter2020]

... dataset is ...

Descriptive statistics on the reviews can be found in `r table_nums("datasets", display = "cite")`. 
All datasets accompanying the systematic reviews are openly published. 
The datasets contain information on all citations obtained in the search strategy and which citations were included in the systematic review.

For every SR, the raw datafiles were preprocessed into a test dataset.

These test datasets contain authors, title, abstract and annotation of whether the entry was included in the final review or not (0/1).

Entries with missing abstracts were removed. 
Duplicate entries were removed. 
Preprocessing scripts can be found on the GitHub repository

@@

### Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets. 
#### ACE
The ACEInhibitors dataset from the study by [@Cohen2006]. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

@@

@@

## Stage 2: simulation
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
### Outcomes 
For each model, 
Several metrics are used to compare performance of different models over datasets,

@@

\newpage

# Results

\newpage
# Discussion

\newpage
# Appendix A - list of definitions

### 2020-03-02 manuscript/test/bookdown-demo.tex
update manuscript and meeting notes

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A Minimal Book Example},
  pdfauthor={Yihui Xie},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{A Minimal Book Example}
\author{Yihui Xie}
\date{2020-02-18}

@@

\hypertarget{strategy}{%
\chapter{Analysis strategy}\label{strategy}}

@@

\begin{itemize}
\tightlist
\item
  ptsd
\item
  ace
\item
  hall
\item
  nagtegaal - van PhD van Lars
\item
  medische van Jan
\end{itemize}

@@

(input table here?)

\begin{itemize}
\tightlist
\item
  Naive Bayes
\item
  Random Forests
\item
  Support Vecor Machine (doc2vec)
\item
  Logistic Regression
\item
  Dense Neural Network (doc2vec)
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Feature extraction = tf-idf
\item
  Query Strategy = max
\item
  Balance Strategy = triple
\item
  n\_instances=10 (number of papers each query)
\item
  n\_prior\_included = 5
\item
  n\_prior\_excluded = 5
\item
  mix\_ratio = 0.95 (95\% max, 5\% random)
\end{itemize}

\hypertarget{hyperparameters}{%
\section{Hyperparameters}\label{hyperparameters}}

@@

\includegraphics{figs/myfirstsim/Figure_1.png}

@@

\includegraphics{figs/myfirstsim/Figure_2.png}

@@

\includegraphics{figs/myfirstsim/Figure_3.png}

@@

\includegraphics{figs/myfirstsim/computation.png}
2191 was best performing with a loss of 0.1124

\includegraphics{figs/myfirstsim/optmizationresult.png}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A Minimal Book Example},
  pdfauthor={Yihui Xie},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{amsthm}
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother
\usepackage[]{natbib}
\bibliographystyle{apalike}

\title{A Minimal Book Example}
\author{Yihui Xie}
\date{2020-02-25}

@@

\hypertarget{introduction-intro}{%
\chapter{Introduction (\#intro)}\label{introduction-intro}}

SR are booming
ML tools as well

\citep{PRISMA-PGroup2015}

What must be the objective of our tool?

Selecting papers is a two-step process: abstract \& fulltext screening

\hypertarget{current-solutions}{%
\section{Current solutions}\label{current-solutions}}

Workload savings 30-70 percent, at a loss of 5\% of relevant studies \citep{Omara-Eves2015}.

\hypertarget{methods-methods}{%
\chapter{Methods (\#methods)}\label{methods-methods}}

Goal: evaluate performance of different models of the ASReview tool.
The screening process is simulated using ASReview, seeing if the original inclusions replicate.
annotated include/exclude

@@

The data consists of five open datasets on systematic reviews from various research areas.
All datasets are openly available.
The raw files were preprocessed. Duplicate entries were removed.
Entries with missing abstracts were removed.
Preprocessing scripts can be found on the GitHub repository

Descriptive statistics on the five systematic reviews can be found in Table Table 1.

\begin{table}

\caption{\label{tab:unnamed-chunk-5}Table  1: Descriptive statistics on articles and resulting datasets for each original systematic review.}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Original study} & \multicolumn{4}{c}{Test collection} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
Dataset & No. studies & No. selected for fulltext screening & No. final inclusions & Inclusion rate (\%) & No. studies in test collection & No. selected for fulltext screening test collection & No. final inclusions in test collection & Inclusion rate in test collection (\%)\\
\midrule
nudging & 2006 & 377 & 100 & 4.99 & 2018 & NA & 118 & 5.85\\
wilson & 3453 & 174 & 26 & 0.75 & 3437 & 174 & 26 & 0.76\\
ptsd & 6185 & 363 & 34 & 0.55 & 5782 & 356 & 38 & 0.66\\
software & 8911 & NA & 106 & 1.19 & 8911 & NA & 104 & 1.17\\
ace & 2544 & NA & 41 & 1.61 & 2544 & NA & 41 & 1.61\\
\bottomrule
\end{tabu}
\end{table}

The inclusion rate is \ldots{} data is imbalanced.
what is the philosophy
False negatives must be avoided \ldots{}
The cost of a false negative outweighs the cost of a false positive.
Note that we assume the oracle/original user to hold the truth.
This is of course not always the case.

@@

Five different models were applied on the data.

\hypertarget{optimizing-hyperparameters}{%
\subsection{Optimizing Hyperparameters}\label{optimizing-hyperparameters}}

Every model has its own hyperparameters.
For every model, the hyperparameters are optimized three times, arriving at three versions of the model:

\hypertarget{the-software}{%
\chapter{The software}\label{the-software}}

ASReview takes the following parameters/arguments:

\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X}
\toprule
  & Configurations\\
\midrule
Models & Naive Bayes, Random Forest, Support Vector Machine, Logistic Regression\\
Query Strategies & Cluster Sampling, Maximum Sampling, Cluster * Maximum  Sampling, Maximum * Uncertainty Sampling, Maximum * Random Sampling, Cluster * Uncertainty Sampling, Cluster * Random Sampling\\
Feature extraction strategies & Doc2Vec, TF-IDF, sbert, embeddingIdf\\
\bottomrule
\end{tabu}

Use these inputs to predict relevance of papers.

\hypertarget{stage-1-hyperparameter-optimization-1}{%
\subsection{Stage 1: hyperparameter optimization}\label{stage-1-hyperparameter-optimization-1}}

We are going to test 5 models on 5 different datasets.

\hypertarget{ace}{%
\subsubsection{ACE}\label{ace}}

The ACEInhibitors dataset from the study by \citep{Cohen2006}. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

\href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in \citep{Cohen2006}. (5x2 crossvalidation). Can we beat this?
The data

\hypertarget{ptsd}{%
\subsubsection{ptsd}\label{ptsd}}

The review\\
The data

\hypertarget{hall}{%
\subsubsection{hall}\label{hall}}

The review \citep{Hall2012}, is reviewed in \citep{Yu2016}.

\hypertarget{nudging}{%
\subsubsection{nudging}\label{nudging}}

The review \citep{Nagtegaal2019}
The data \citep{Nagtegaal2019a}

Paper says:
- systematic search n = 2006
- full text screening n = 377
- included in synthesis n = 100

Open data online says:

\begin{itemize}
\tightlist
\item
  systematic search n =
\item
  full text screening n =
\item
  included in synthesis n = 101 (18?)
\end{itemize}

abstract excel sheet private says:
- systematic search n = 2018
- full text screening n =
- included in synthesis n = 118

Difference in 18 inclusions = systematic reviews. to exclude/include?

\hypertarget{wilson}{%
\subsubsection{Wilson}\label{wilson}}

The review \citep{Appenzeller-Herzog2019}
The dataset \citep{Appenzeller-Herzog2020}

\begin{itemize}
\tightlist
\item
  systematic search n = 3453
\item
  full text screening n = 174
\item
  included in synthesis n = 26
\end{itemize}

\hypertarget{models-1}{%
\subsection{Models}\label{models-1}}

\begin{itemize}
\tightlist
\item
  Naive Bayes
\item
  Random Forests
\item
  Support Vecor Machine
\item
  Logistic Regression
\item
  Dense Neural Network
\end{itemize}

Or, more specific:

\begin{tabular}{ll}
\toprule
Models & Feature extraction strategies\\
\midrule
nb & tfidf\\
rf & tfidf\\
svm & tfidf\\
lr & doc2vec\\
NA & NA\\
\bottomrule
\end{tabular}

@@

\begin{itemize}
\tightlist
\item
  Query Strategy = max
\item
  Balance Strategy = triple
\item
  n\_instances=10 (number of papers each query)
\item
  n\_prior\_included = 5
\item
  n\_prior\_excluded = 5
\end{itemize}

\hypertarget{hyperparameters}{%
\subsection{Hyperparameters}\label{hyperparameters}}

Every model has its own set of hyperparameters:

\hypertarget{optimization}{%
\subsection{Optimization}\label{optimization}}

The hyperparameters are optimized on the 5 datasets in three different ways:

\begin{itemize}
\tightlist
\item
  1 on 1: maximum performance
\end{itemize}

\[ d = D \]
- 4 on 1: cross-validation
\[ d \notin D\]

\[ D = {1, 2, 3, 4}\]

\begin{itemize}
\tightlist
\item
  5 on 1: more data = more better?
\end{itemize}

\[ d \in D \]

\hypertarget{stage-2-simulation-1}{%
\section{Stage 2: simulation}\label{stage-2-simulation-1}}

\hypertarget{outcomes}{%
\subsection{Outcomes}\label{outcomes}}

Several metrics are used to compare performance of different models over datasets,

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\begin{minipage}[b]{0.29\columnwidth}\raggedright
Dataset\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Naive Bayes\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Random Forests\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Support Vector Machine\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Logistic Regression\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Dense Neural Network\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.29\columnwidth}\raggedright
ptsd\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
ace\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
hall\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
nagtegaal\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
\ldots.\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

? How to compare outcomes of 3 different optimization strategies?

\hypertarget{evaluation}{%
\section{Evaluation}\label{evaluation}}

@@

\includegraphics[width=17.78in]{figs/myfirstsim/Figure_1}

@@

\includegraphics[width=17.78in]{figs/myfirstsim/Figure_2}

@@

\includegraphics[width=17.78in]{figs/myfirstsim/Figure_3}

@@

\includegraphics[width=26.42in]{figs/myfirstsim/computation}
2191 was best performing with a loss of 0.1124

\includegraphics[width=23in]{figs/myfirstsim/optmizationresult}

@@

  \bibliography{book.bib,packages.bib}
